\documentclass{edelgas-resume}

\setmainfont[
 Ligatures=TeX,
 BoldFont={Charter Bold}, 
 ItalicFont={Charter Italic},
 BoldItalicFont={Charter Bold Italic},
 ]{Charter}

\setsansfont[
 Ligatures=TeX,
 BoldFont={Charter Bold}, 
 ItalicFont={Charter Italic},
 BoldItalicFont={Charter Bold Italic},
 Scale=MatchLowercase
]{Charter}

%Custom Variables
\newcommand*{\name}{Alex Chalk} 
\newcommand*{\github}{github.com/AlexChalk} 
\pagestyle{empty} % Removes page number


%if desired, this will create a really nice customized footer
\newcommand{\foot}{
%{\name} --- \thepage\ of \pageref{LastPage}
Alex Résumé --- Page \thepage\ of \pageref{LastPage}
}

\begin{document}
%Header
\namehead%prints your name
\githubhead%prints your github handle
\address{7-6575 Rue Saint-Urbain, Montréal, QC, H2S 3G6, Canada}{+1 (514) 549-5327}{contact@alexchalk.net}


% Programmer Bio
\sectionheading{Bio}
\vspace{-1.8em}
{\fontsize{10}{15}\selectfont{\setlength{\parindent}{0pt}\justify{Strong on research, planning, coordinating with partners. The fastest ever dev to complete an ebanx (payment provider) integration last time I checked. Not the best at moving fast and breaking things (I value transparency). Love tmux, vim, static fp. Rely on data, high impact social goals for max motivation. I was a freelance editor once; I write great docs!\par}}}
\vspace{1em}


%Business Experience
\sectionheading{Professional Experience}

\organization{Busbud}{Montréal, Canada}{2018--20}
\begin{position}{Fullstack Developer}{}
	\item Node.js, TypeScript, PostgreSQL, RabbitMQ, Kubernetes, Terraform, Docker.
  \item Integration of supply, tooling, post-purchase/payment features, planning.
  \item Sold world's largest bus trip inventory to millions of unique annual users.

\end{position}

\organization{Roof Ai}{Montréal, Canada}{2017--18}
\begin{position}{Fullstack Developer}{}
\item Webpack, React, Redux, MongoDB, Express.js.
\item Automated real-estate lead conversation using chatbots.

\end{position}


\organization{Makers Academy}{London, U.K. (Remote)}{2017}
\begin{position}{Full-time Student}{}
\item TDD, pair-programming, Agile/Scrum, OOP, SOLID, Ruby, Javascript.
\item Europe's most selective coding bootcamp; an intensive 16-week course.

\end{position}

\organization{Growth Compass Marketing}{Wakefield, Canada (Remote)}{2015--17}
\begin{position}{Editor and Copywriter}{}
\item Research and written content for clients and campaigns.
\item Marketing consultancy working in engineering and technology.

\end{position}


%Education
\sectionheading{Education}

\organization{University of Oxford}{Oxford, U.K.}{2011--14}
\begin{position}{B.A. Philosophy and Theology}{}
\item First Class Honours Degree (highest possible grade, GPA 4.0).
\item Choral Scholar with Mansfield College Chapel Choir.
\end{position}

%Skills
\sectionheading{Other}
\vspace{-1em}
Fluent in French. Sing in Choir of St Andrew \& St Paul.\hfill{\itshape{References available upon request.}}

\end{document}
